\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Warm-Up 12}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Formula Area}

\begin{enumerate}
\item Mean of a \textbf{uniform distribution} from $a$ to $b$: $\mu = (a+b)/2$
\item Standard deviation of a \textbf{uniform distribution} from $a$ to $b$: $\sigma = \sqrt{(b-a)^2/12}$
\item The normalized pdf of a \textbf{uniform distribution} from $a$ to $b$ is $p(x) = 1/(b-a)$.
\item The IQR, or interquartile range, is $Q3 - Q1$.
\end{enumerate}

\section{Uniform Distribution, PDFs}

\begin{enumerate}
\item Births are approximately uniformly distributed between the 52 weeks of the year. They can be said to follow a uniform
distribution from one to 53 (spread of 52 weeks).  Use this fact to answer below:
\begin{itemize}
\item Graph the normalizeed pdf. What is $p(x)$, the normalized pdf? \\ \vspace{1.5cm}
\item What are the mean and standard deviation of this distribution? \\ \vspace{1cm}
\item What is the probability someone is born between weeks 2 and 12? \\ \vspace{1cm}
\item What is the probability that someone is born on exactly on Christmas morning, week 52.0? \\ \vspace{1cm}
\item Find the 70th percentile. \\ \vspace{1cm}
\end{itemize}
\item Suppose that the value of a stock varies each day from \$16 to \$25 with a uniform distribution.
\begin{itemize}
\item Find the upper quartile - 25\% of all days the stock is above what value? Draw the graph. \\ \vspace{1.5cm}
\item Find the lower quartile, and the IQR.
\end{itemize}
\end{enumerate}

\end{document}