\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Warm-Up 7}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Formula Area}

\begin{itemize}
\item \textit{N}: Usually $N$ refers to the size of a data set.
\item \textit{Frequency:} The number of times a particular value occurs in a data set.
\item \textit{Relative frequency:} The frequency divided by $N$.
\item \textit{Qualitative or categorical data}: Data properties that are not countable, \textit{e.g.} hottest chile species.
\item \textit{Quantitative discrete data:} Data properties that are countable but not continuous (rational) numbers.
\item \textit{Quantitative continuous data:} Data properties that are countable and continuous (rational).
\item A \textit{histogram} is a bar-chart of frequencies or relative frequencies on the y-axis, with the categories or bins on the x-axis.
\item The mean $\bar{x}$ of a sample is 
\begin{equation}
\bar{x} = N^{-1} \sum_{i=1}^N x_i = \sum_{i=1}^M f_{r,i} x_i
\end{equation}
where $N$ is the size of the data set, $M$ is the number of bins, and $f_{r,i}$ are the relative frequencies.
\item \textit{Median:} A value that separates half of the data set above it, and half below it.
\item \textit{Quartiles:} $Q1$, $Q2$, and $Q3$ are values that separate the data into four equal frequencies.
\item The standard deviation $s$ of a sample is given by
\begin{equation}
s^2 = (N-1)^{-1} \sum_{i=1}^N (x_i-\bar{x})^2 = \bar{x^2} - \bar{x}^2
\end{equation}
where $N$ is the size of the data set, and $M$ is the number of bins.
\end{itemize}

\section{Unit 0 Review and Warm-up}

\begin{enumerate}
\item What type of data is \textbf{number of hours of sleep per night?}
\item Suppose a sample of hours per night of sleep is ${4,4,5,5,6,7,8,8}$ for a person.  Answer the following:
\begin{enumerate}
\item What is the mean and standard deviation of the data set? How many standard deviations below the mean is the first data point? \\ \vspace{0.33cm}
\item What is the median or $Q2$ of the data set? \\ \vspace{0.33cm}
\item What are the quartiles of the data set? \\ \vspace{0.33cm}
\item Draw a time-series of the data set.
\end{enumerate}
\end{enumerate}

\end{document}