\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Warm-Up 13}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Formula Area}

\begin{enumerate}
\item Normal distribution PDF: $p(x) = \frac{1}{\sqrt{2\pi \sigma^2}} \exp\left( -\frac{1}{2}(x-\mu)^2/\sigma^2 \right)$
\item The \textit{z-score} of a particular event $x$ drawn from a normal distribution is $z = (x-\mu)/\sigma$.
\item Probabilities for a normal distribution: $p(-1\sigma < x < 1\sigma) = 0.68$, $p(-2\sigma < x < 2\sigma) = 0.95$, and $p(-3\sigma < x < 3\sigma) = 0.997$.
\end{enumerate}

\section{Normal Distribution, PDFs}

\begin{enumerate}
\item The patient recovery time from a particular surgical
procedure is normally distributed with a mean of 5.3 days and a standard deviation of 2.1 days. Which of the following is the median recovery time?
\begin{itemize}
\item A: 5.3 days
\item B: 2.9 days
\item C: 2.1 days
\item D: 1.0 days
\end{itemize}
\item What is the z-score for a patient who takes 11.6 days to recover?
\begin{itemize}
\item A: 2.0
\item B: 3.0
\item C: 3.5
\item D: 4.5
\end{itemize}
\item The systolic blood pressure (given in millimeters) of males has an approximately normal distribution with mean $\mu = 125$ and standard deviation $\sigma = 14$. Systolic blood pressure for males follows a normal distribution. (a) What blood pressure corresponds to a result that is $2\sigma$ above the mean? (b) What is the probability that someone has a blood pressure of 153 millimeters? (c) Draw the blood pressure distribution below. \\ \vspace{2cm}
\item A certain radar system can hear a radio-frequency reflection with a minimum \textit{signal-to-noise ratio} (SNR) of 3.0.  The signal is hidden in random radio noise, that has units of voltage.  The amplitude of the noise voltages are approximately normally distributed, with $\mu = 0$ Volts, and $\sigma = 0.03$ Volts.  In this case, the SNR is essentially the voltage of the signal divided by $\sigma$.  What is the minimum signal echo voltage the radar needs to make a detection?
\end{enumerate}

\end{document}