\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}

\begin{document}

\title{Warm-Up 18}
\author{Prof. Jordan C. Hanson}

\maketitle

\section{Formula Area}

\begin{enumerate}
\item The normal distribution pdf is $\frac{1}{\sqrt{2\pi \sigma^2}} \exp(-0.5(x-\mu)^2/\sigma^2)$
\item Recall the 68 - 95 - 99.7 rule.
\item Recall that the \textit{area under the pdf} is the probability.  The total area is 1, and the area between points $a$ and $b$ is less than one, or a fraction of the total probability.
\end{enumerate}

\section{Reviewing the normal distribution}

\begin{enumerate}
\item What is the probability a measurement is within 3 standard deviations from the mean of its underlying normal distribution (pdf)?  That is, \textit{above or below} the mean by three or fewer standard deviations?
\begin{itemize}
\item A: 68 percent
\item B: 95 percent
\item C: 99.7 percent
\item D: 34 percent
\end{itemize}
\item What is the probability a measurement is 1 standard deviation \textbf{away from} the mean of its underlying normal distribution (pdf)?  That is, \textit{above} or \textit{below} the mean by one standard deviation?
\begin{itemize}
\item A: 32 percent
\item B: 5 percent
\item C: 0.3 percent
\item D: 15 percent
\end{itemize}
\item What is the probability a measurement is 1 standard deviation \textbf{larger than} the mean of its underlying normal distribution (pdf)?  That is, \textit{above} the mean by one standard deviation?
\begin{itemize}
\item A: 68 percent
\item B: 95 percent
\item C: 32 percent
\item D: 16 percent
\end{itemize}
\item What is the probability a measurement is 2 standard deviations \textbf{larger than} the mean of its underlying normal distribution (pdf)?  That is, \textit{above} the mean by two standard deviations?
\begin{itemize}
\item A: 1 percent
\item B: 2 percent
\item C: 2.5 percent
\item D: 10 percent
\end{itemize}
\end{enumerate}

\end{document}